Pre-/Post-Trikafta in CFRD

### 2022-02-02 Christine Chan/Pre-post Trikafta/pre_post_trikafta_analysis.Rmd
Update pre_post_trikafta_analysis.Rmd

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "B:/Projects"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Laura/BDC/Projects"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Laura/BDC/Projects"
}
knitr::opts_knit$set(root.dir = home_dir)
```

```{r}

```

>>>>

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
}
knitr::opts_knit$set(root.dir = home_dir)
```

```{r}
# Import cleaned data from Casey
df = read.csv("./Christine Chan/Prepost Triakfta/Data_Cleaned/analysis_data.csv",na.strings = "NA")
df$X = NULL
# Fill in MRN and CFF ID for everyone
df = df %>% 
  group_by(CFF.ID) %>% fill(MRN,.direction = "downup") %>% 
  group_by(MRN) %>% fill(CFF.ID,.direction = "downup") %>%
  arrange(CFF.ID,Date)
# Fill in constant variables for all rows
df = df %>% group_by(MRN) %>% fill(CFF.ID,.direction = "downup") %>% 
  group_by(CFF.ID) %>% fill(DOB,Start:Genotypes2,CFRD.Diagnosis.Date,.direction = "downup")
# Remove those without a start date
t = df %>% filter(is.na(Start)) %>% select(CFF.ID,site)
```

```{r}
# Piecewise model function
piecewise = function(outcome,data = df){

}
```
